% LaTeX Resume Pandoc Template jb2resume.latex
%
% Copyright (c) 2016-2017, John Bokma
% Based on Jason Blevins' LaTeX CV Template;
% http://jblevins.org/projects/cv-template/
%
% GitHub: https://github.com/john-bokma/resume-pandoc

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{underscore}
\usepackage[parfill]{parskip}
\usepackage{lmodern}
\usepackage[svgnames]{xcolor}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Your name on the resume
\def\name{Kae Job Sluder}

% The following metadata will show up in the PDF properties
\hypersetup{
colorlinks = true,
urlcolor=blue,
linkcolor=magenta,  
 pdfauthor = {\name},
pdfkeywords = {java, python, html5, javascript, instructional design,
full-stack development},
pdftitle = {\name: Curriculum Vitae},
pdfsubject = {Curriculum Vitae},
pdfpagemode = UseNone
}

\geometry{
body={6.5in, 9.0in},
left=1.0in,
top=1.0in
}

% Fix for "! Undefined control sequence. <recently read> \tightlist",
% see: https://github.com/osener/markup.rocks/issues/4
% I have this issue with Pandoc 1.17.2
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Page number is top right, and it is possible to control the rest of
% the header.
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Section numbers or not (default)
\setcounter{secnumdepth}{0}

% By putting an empty \item[] at the start of the list, the list
% starts on a new line.
\setlist[itemize]{leftmargin=1em,label={--},before=\item[]}

\setlist[description]{leftmargin=0em, style=sameline}

% Don't use monospace font for URLs
\urlstyle{same}

\begin{document}

% Place name at left
{\huge \name}

\bigskip

\begin{minipage}[t]{0.495\textwidth}
Email: <kaesluder@fastmail.com> \\ LinkedIn:
[www.linkedin.com/in/kae-sluder](https://www.linkedin.com/in/kae-sluder/)
\end{minipage} % Don't use empty lines after \end and the next \begin{minipage}.
\begin{minipage}[t]{0.495\textwidth}
Personal Site:
[kaesluder.github.io](https://kaesluder.github.io/) \\ Pronouns:
they/them
\end{minipage}

# Summary

Full-stack Java and Python programmer, experienced instructional
designer, and client-centered solution finder.

# Skills

- **Programming Languages:** Java, Python, JavaScript
- **Service Development:** AWS Microservices, Spring
- **Front-End Development:** HTML, CSS, JavaScript, React, Web
  Components
- **Databases:** postgresql, SQLite, DynamoDB

# Work Experience

## Amazon -- Software Engineering Intern

**2023 - present:** remote

- Prototyped database service for 2-factor authentication with
  expected delivery to millions of customers.
- Deployed code to microservices framework using CI and continuous
  testing frameworks targeting %99.9 availability.
- Developed APIs and wrapper libraries to connect multiple services to
  provide an easy 2-factor experience for customers.
- Participated in code reviews and planning sessions for long-term
  feature rollout.

## Ada Developer's Academy -- Student Software Engineer

**2022 - present:** remote

- Developed APIs using Python and Flask.
- Developed data-driven Single-Page Application front-ends using
  JavaScript and React.
- Created multi-platform applications using Python, WebKit, and
  JavaScript
- Collaborated on projects using pair programming, code reviews, and
  test-driven development.
- Maintained development repositories in Git and GitHub.

## Savannah College of Art and Design -- Instructional Designer

**2008 - 2020:** Savannah, GA

- Developed student-centered curriculum design for Photographic Arts
  MA and MFA sequence.
- Redesigned online Historic Preservation and Adaptive Reuse program.
- Developed multiple online courses and course revisions for
  Interactive Technology and Game Design curriculum.
- Supported instructors in shift to virtual teaching during COVID
  operations.
- Developed more than 80 fully online and hybrid courses using
  Blackboard and HTML.
- Performed final integration and deployment for courses.
- Worked with instructors and department stakeholders to ensure that
  courses met quality and curriculum goals.

# Education

## Indiana University, Bloomington

**Instructional Systems Technology, M.S. 1997; PhD 2010**

- Used Social Network Analysis and Discourse Analysis to examine
  gender equity in a K-12 virtual learning environment.
- Applied Discourse Analysis in a study of student teacher experience
  and community identification.
- Documentary filming of inquiry-based and student-centered classrooms
  for teacher professional development service.
- Provided instructional technology support in multimedia classrooms
  to instructors.

**Microbiology, B.S. 1994**

- Independent study of light-triggered Selenium toxicity in _C.
  reinhardtii_

# Volunteer Experience

## First City Pride Center, Savannah, GA -- Front Desk Volunteer

**2019 -- 2022**

- Connected walk-in visitors to services and information.
- Facilitated hybrid and virtual support-group meetings
- Planned and organized small-group programming and events.
- Organized clothing swap to provide donated clothes to trans people
  in local community.
- Provided rapid HIV testing and HIV prevention counseling.

\end{document}
